---
title: "BIAAQ 5 using GAabbreviate"
output: html_notebook
---
QUESTIONNAIRE BACKGROUND

The Body Image Acceptance and Action Questionnaire is a 12 item measure.
It assesses psychological flexibility in relation to one's body image. 
The code presented here was used for the publication Basarkod, Sahdra, & Ciarrochi (2017). 
In-press version of the article available here: tinyurl.com/BI-AAQ-5-GA

ITEMS: 
 1. Worrying about my weight makes it difficult for me to live a life that I value.
 2. I care too much about my weight and body shape
 3. I shut down when I feel bad about my body shape or weight.
 4. My thoughts and feelings about my body weight and shape must change before I can take important steps in my life.
 5. Worrying about my body takes up too much of my time.
 6. If I start to feel fat, I try to think about something else. 
 7. Before I can make any serious plans, I have to feel better about my body.
 8. I will have better control over my life if I can control my negative thoughts about my body.
 9. To control my life, I need to control my weight.
 10. Feeling fat causes problems in my life.
 11. When I start thinking about the size and shape of my body, it's hard to do anything else.
 12. My relationships would be better if my body weight and/or shape did not bother me.

Each item is rated on a scale of 1 (Never true) to 7 (Always true), with higher scores indicative of lower psychological flexibility. 


###Packages and Training Sample
```{r}

#LOAD LIBRARIES
library(foreign)
library(stats) 
library(dplyr) 
library(lavaan)
library(GAabbreviate) 
library(sjPlot)
library(semTools)

#WORKING DIRECTORY
setwd("C:/Users/z3527373/OneDrive/Other Academic Stuff/GA Workshop")

#SAMPLE ONE - TRAINING SAMPLE
#Load dataset
Data1 <- read.csv("GAData1.csv", stringsAsFactors = F, header = T) #general population American sample collected via Survey Monkey

#Remove outliers in age
Data1 <-filter(Data1, Age > 17)
Data1 <- filter(Data1, Age < 66)
dim(Data1) #538*38

```


###Genetic algorithm
```{r}
#The complete set of items you want to run the GA on (All items from the original 12-item BI-AAQ).
#Items are not reverse scored here, but since all 12 items are reversed, results of the GA will be the same with or without using reversed scores.
#If a combination of reversed and non-reversed scores, make sure to reverse score items before using GAabbreviate

Bitems <- c("BIAAQ1", "BIAAQ2", "BIAAQ3", "BIAAQ4", "BIAAQ5", "BIAAQ6",
            "BIAAQ7", "BIAAQ8", "BIAAQ9", "BIAAQ10", "BIAAQ11", "BIAAQ12")

#Create dataset with chosen variables. 12 variables in this case.
Items <- Data1[,Bitems]

#Because of recent R and R package updates, you need to remove column names before proceeding. 
#You can still know which items the GA has chosen without column names. 
colnames(Items) <- NULL 

#Set number of subscales. ncol = 1 in this case as there is only one subscale.
Scale <- matrix(rowSums(Items), ncol = 1) 

#FOR A QUESTIONNAIRE WITH MULTIPLE SUBSCALES
#items = matrix(sample(1:5, nsubject*nitems, replace = TRUE), nrow = nsubject, ncol = nitems)
#scales = cbind(rowSums(items[,1:10]), rowSums(items[,11:15])
               

#RUN GA
#Set the seed, so that your output it the same every time you run it.  
set.seed(100) #You can also set seed within the GAabbreviate function, but doing this beforehand is more precise. 

#You can run several trial runs by varying itemCost, maxItems, popSize, maxiter, etc.
#Refer to Sahdra, Ciarrochi, Parker & Scrucca (2016) for an example of how to use GAabbreviate.
#Call ?GAabbreviate to see the help file. 
BGA <- GAabbreviate(Items, Scale, itemCost = 0.01, maxItems = 12,
                    maxiter = 200, run = 100, popSize=200, verbose = T, crossVal = F, plot = T) 

#GET RESULTS OF GA
summary(BGA)
plot(BGA)

#Mean variance explained by the short form
BGA$results$meanR2 # 0.96

# alphas of the subscale of the short form
BGA$measure$alpha #0.91

#Items in the 5-item short form
BGA$measure$items #Items 1, 3, 4, 8, 10

# more detailed information about the GA run settings and results
BGA$measure
BGA$results
BGA$best

```

###Cross-validation sample prep
```{r}
#Load dataset
Data2 <- read.csv("GAData2.csv", stringsAsFactors = F, header = T) #general population American sample collected via Survey Monkey

#Filter outliers in age.
Data2 <-filter(Data2, Age > 17)
Data2 <- filter(Data2, Age < 66)
dim(Data2) #762*93

#Prepare data for analyses

#Reverse coding of items
#For the Body Image - Acceptance and Action Questionnaire
Data2$BIAAQ1R  <- 8 - Data2$BIAAQ1
Data2$BIAAQ2R  <- 8 - Data2$BIAAQ2
Data2$BIAAQ3R  <- 8 - Data2$BIAAQ3
Data2$BIAAQ4R  <- 8 - Data2$BIAAQ4
Data2$BIAAQ5R  <- 8 - Data2$BIAAQ5
Data2$BIAAQ6R  <- 8 - Data2$BIAAQ6
Data2$BIAAQ7R  <- 8 - Data2$BIAAQ7
Data2$BIAAQ8R  <- 8 - Data2$BIAAQ8
Data2$BIAAQ9R  <- 8 - Data2$BIAAQ9
Data2$BIAAQ10R <- 8 - Data2$BIAAQ10
Data2$BIAAQ11R <- 8 - Data2$BIAAQ11
Data2$BIAAQ12R <- 8 - Data2$BIAAQ12

#For the Self Compassion Scale - Short Form
Data2$SCS1R  <- 6 - Data2$SCS1
Data2$SCS4R  <- 6 - Data2$SCS4
Data2$SCS8R  <- 6 - Data2$SCS8
Data2$SCS9R  <- 6 - Data2$SCS9
Data2$SCS11R <- 6 - Data2$SCS11
Data2$SCS12R <- 6 - Data2$SCS12

#Column Names with the items for each measure
BSQ.colnames   <- c("BSQ1", "BSQ2", "BSQ3", "BSQ4", "BSQ5", "BSQ6", "BSQ7", "BSQ8") #Body Shape Questionnaire - 8C
BIAAQ.colnames <- c("BIAAQ1R", "BIAAQ2R", "BIAAQ3R", "BIAAQ4R", "BIAAQ5R", "BIAAQ6R",
                    "BIAAQ7R", "BIAAQ8R", "BIAAQ9R", "BIAAQ10R", "BIAAQ11R", "BIAAQ12R") #Body Image - Acceptance and Action Questionnaire
BIAAQ5.colnames<- c("BIAAQ1R", "BIAAQ3R", "BIAAQ4R","BIAAQ8R", "BIAAQ10R") #5-item short form of the BI-AAQ 
BSSI.Colnames  <- c("BSSI1", "BSSI2", "BSSI3", "BSSI4", "BSSI5", "BSSI6", "BSSI7", "BSSI8", "BSSI9", "BSSI10") #Brief Situations of Stigma Inventory
SCS.colnames   <- c("SCS1R", "SCS2", "SCS3", "SCS4R", "SCS5", "SCS6", "SCS7", "SCS8R", "SCS9R", "SCS10", "SCS11R", "SCS12R") #Self-Compassion Scale - Short Form
SATAQ.Muscle   <- c("SATAQ1", "SATAQ2", "SATAQ6", "SATAQ7", "SATAQ10") #Thin internalisation subscale of the Sociocultural Attitudes Towards Appearance Questionnaire-4
SATAQ.Thin     <- c("SATAQ3", "SATAQ4", "SATAQ5", "SATAQ8", "SATAQ9") #Muscle internalisation subscale of the Sociocultural Attitudes Towards Appearance Questionnaire-4
GHQ.colnames   <- c("GHQ1", "GHQ2", "GHQ3", "GHQ4", "GHQ5", "GHQ6", "GHQ7", "GHQ8", "GHQ9", "GHQ10", "GHQ11", "GHQ12") #General Health Questionnaire - 12

#Scoring the measures
Data2$Diss   <- rowSums(Data2[,colnames(Data2) %in% BSQ.colnames]) #This is RowSums so that you can create a subset of people scoring 19 and over. 
Data2$Flex   <- rowMeans(Data2[,colnames(Data2) %in% BIAAQ.colnames])
Data2$Flex5  <- rowMeans(Data2[,colnames(Data2) %in% BIAAQ5.colnames])
Data2$Stigma <- rowMeans(Data2[,colnames(Data2) %in% BSSI.Colnames])
Data2$Comp   <- rowMeans(Data2[,colnames(Data2) %in% SCS.colnames])
Data2$Thin   <- rowMeans(Data2[,colnames(Data2) %in% SATAQ.Thin])
Data2$Muscle <- rowMeans(Data2[,colnames(Data2) %in% SATAQ.Muscle])
Data2$GHQ    <- rowMeans(Data2[,colnames(Data2) %in% GHQ.colnames])


dim(Data2) #762x119 

```



###Cross-validation analyses
```{r}
#Confirmatory Factor Analyses to test factor structure of both the long and short form BI-AAQ

#BI-AAQ 12 items

CFABIAAQ <- ' Flex =~ BIAAQ1R + BIAAQ2R + BIAAQ3R + BIAAQ4R + BIAAQ5R + BIAAQ6R + BIAAQ7R + BIAAQ8R 
+ BIAAQ9R + BIAAQ10R + BIAAQ11R + BIAAQ12R'

fit.model12<- cfa(CFABIAAQ, data=Data2, mimic="Mplus", estimator="MLR")
summary(fit.model12, fit.measures = TRUE)
#CFI = .96; TLI = .95; RMSEA = .071 [.065 .078]


#BI-AAQ-5 items

CFABIAAQ5 <- 'Flex =~ BIAAQ1R + BIAAQ3R + BIAAQ4R + BIAAQ8R + BIAAQ10R'

fit.model5<- cfa(CFABIAAQ5, data=Data2, mimic="Mplus", estimator="MLR")
summary(fit.model5, fit.measures = TRUE)
#CFI = .98; TLI = .96; RMSEA = .083 [.063 .104]


#Omega estimates
#BI-AAQ
Full <- Data2[c("BIAAQ1R", "BIAAQ2R", "BIAAQ3R", "BIAAQ4R", "BIAAQ5R", "BIAAQ6R",
                "BIAAQ7R", "BIAAQ8R", "BIAAQ9R", "BIAAQ10R", "BIAAQ11R", "BIAAQ12R")]
set.seed(1)
MBESS::ci.reliability(data=Full, type="omega", conf.level = 0.95, interval.type="bca", B=1000)
#est = 0.963, SE = 0.002, 95% CI = 0.959-0.968

#BI-AAQ-5
Short <- Data2[c("BIAAQ1R", "BIAAQ3R", "BIAAQ4R","BIAAQ8R", "BIAAQ10R")]
set.seed(1)
MBESS::ci.reliability(data=Short, type="omega", conf.level = 0.95, interval.type="bca", B=1000) 
#est = 0.933, SE = 0.005, 95% CI = 0.923-0.942


#Alphas
#12-item BI-AAQ
psych::alpha(Data2[ ,c("BIAAQ1R", "BIAAQ2R", "BIAAQ3R", "BIAAQ4R", "BIAAQ5R", "BIAAQ6R",
                          "BIAAQ7R", "BIAAQ8R", "BIAAQ9R", "BIAAQ10R", "BIAAQ11R", "BIAAQ12R")])

#5-item BI-AAQ-5
psych::alpha(Data2[ ,c("BIAAQ1R", "BIAAQ3R", "BIAAQ4R","BIAAQ8R", "BIAAQ10R")])

#Correlations
sjt.corr(Data2[c("Flex", "Flex5", "Age", "BMI", "Diss", "Stigma", "Thin", "Muscle", "Comp", "GHQ")] ,
         corr.method = "pearson",
         na.deletion = "pairwise",
         p.numeric = FALSE,  # significance levels are indicated by asterisks
         show.p = TRUE,      # show exact pvalues
         triangle = "lower",
         digits = 2# print the values in the lower triangle of the table
         )


```

